Data preparation for employee category analysis

### 2023-04-27 04. Analysis/scripts/02_data_preparation_clusters_employee.Rmd
Update 02_data_preparation_clusters_employee.Rmd
Adding notes, working more on onsite minimum

```{r}
prep_a <- 
  tibble(
  date = seq.Date(from = ymd("2022-01-01"),
         to = ymd("2022-12-31"),
         by = "2 weeks")
) %>% 
  rownames_to_column(var = "period_number") 
# %>% 
#   mutate(
#     date_pay_period_start_lead = lead(date_pay_period_start)
  # )
```

@@

```{r}
prep_c <- 
  prep_b %>% 
  left_join(prep_a) %>% 
  fill(period_number, .direction = "down")
```

@@

@@

```{r}
prep_e %>% 
  filter(daily_status_imputed == "Reporting to Job Site") %>% 
  mutate(
    telework_onsite_minimum = case_when(days >= 2 ~ 1,
                                        TRUE ~ 0)
  ) %>% 
  group_by(person_id) %>% 
  summarise(
    telework_onsite_minimum = mean(telework_onsite_minimum)
  )
```

@@

>>>>

```{r}
prep_a <- 
  tibble(
  date = seq.Date(from = ymd("2022-01-01"),
         to = ymd("2022-12-31"),
         by = "2 weeks")
) %>% 
  rownames_to_column(var = "period_number") 
```

Second, create a dataframe of all the days of the year.

@@

Third, left join the pay periods dataframe (`prep_a`) to the days of the year (`prep_b`), then fill the null `period_number` values with the entry above.
```{r}
prep_c <- 
  prep_b %>% 
  left_join(prep_a) %>% 
  fill(period_number, .direction = "down")
```

@@

```{r}
prep_f <- 
  prep_e %>% 
  filter(daily_status_imputed == "Reporting to Job Site") %>% 
  mutate(
    telework_onsite_minimum = case_when(days >= 2 ~ 1,
                                        TRUE ~ 0)
  ) %>% 
  group_by(person_id) %>% 
  summarise(
    telework_onsite_minimum_mean = mean(telework_onsite_minimum)
  ) %>% 
  ungroup() %>% 
  mutate(
    telework_onsite_minimum = case_when(telework_onsite_minimum_mean == 1 ~ 1,
                                        TRUE ~ 0)
  )
```

@@

@@

### Position description categories

```{r}
prep_a <- 
  cohort_first %>% 
  select(person_id,position_category_description) %>% 
  character_to_indicator(in_unique_identifier = person_id,
                         position_category_description,
                         in_prefix = "rules_based_position_category_")
```
